Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-15 chapters/introduction/introduction.tex
background geo-calibration

\subsection{Geo-Calibration}
%\todo{add deterministic methods}
%
Automatic image geo-calibration continues to grow in importance as a
direct result of the increasing amount of imagery available
via the Internet. Conceptually geo-calibration task is
straightforward: given an image, identify the time and the location it
was captured in the world and the direction the camera was facing.
Solving this problem is of great value for a wide variety of fields,
with potential applications ranging from the forensic
sciences~\cite{stylianou13jane} to crowd-sourced environmental
monitoring~\cite{zhang2012mining}.

Extracting location-dependent or orientation-dependent features from
image data has drawn a great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{hays2008im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch et al. extract location-dependent features that
capture the relative appearance differences of large cities.  Lin et
al.~\cite{lin2013cross} localize a ground-level image by learning the
relationship between pairs of ground and aerial images of the same
location. Other techniques focus on urban environments and infer
location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
estimate camera pose. Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.
For time estimation, Matzen and Snavely~\cite{matzen2014scene} predict
timestamps for photos by matching against a time-varying
reconstruction of a scene.  Hill~\cite{hill1994elephant} estimate the
time of the day by analyze the light intensity profiles captured by
cameras.

However, recognizing the geo-location and geo-orientation of an
arbitrary outdoor image is an extremely challenging task.  Many
methods have been proposed; the most common approach is to build a
large database of images with known location and localize a query
image using either local~\cite{li2010location,schindler2008detecting}
or global~\cite{hays2008im2gps,doersch2012what} image features. 
%This approach is not applicable when no nearby ground-level imagery
%exists in the reference database, such as when the image was not
%captured near a popular tourist destination.  Even when reference
%imagery is available, the appearance of the objects may not be
%visually distinctive, for example a train track or a body of water.

>>>>

\subsection{Geo-Calibration}
%\todo{add deterministic methods}
%
Automatic image geo-calibration continues to grow in importance as a
direct result of the increasing amount of imagery available
via the Internet. Conceptually the geo-calibration task is
straightforward: given an image, identify the time and the location it
was captured in the world and the direction the camera was facing.
Solving this problem is of great value for a wide variety of fields,
with potential applications ranging from the forensic
sciences~\cite{stylianou13jane} to environmental
monitoring~\cite{zhang2012mining}.

\begin{itemize}[noitemsep]
\item \textbf{Geo-Localization:}
Extracting location-dependent or orientation-dependent features from
image data has drawn a great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{hays2008im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch \etal~\cite{doersch2012what} extract
location-dependent features that capture the relative appearance
differences of large cities.  Lin et al.~\cite{lin2013cross} localize
a ground-level image by learning the relationship between pairs of
ground and aerial images of the same location. Other techniques focus
on urban environments and infer location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
estimate camera pose. Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.
\newline

\item \textbf{Time Estimation:}
Matzen and Snavely~\cite{matzen2014scene} predict
timestamps for photos by matching against a time-varying
reconstruction of a scene.  Hill~\cite{hill1994elephant} estimate the
time of the day by measuring the light intensity profiles captured by
cameras.~\cite{salem2016face2year,ginosar2015century} propose to date the
year book photos by analyzing human appearance. Lee
\etal~\cite{linking2015iccp} find visual paterns in the buildings,
relate them to certain time periods.
